---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# simulationmachine

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/kasaai/simulationmachine.svg?branch=master)](https://travis-ci.org/kasaai/simulationmachine)
<!-- badges: end -->

**NOTE: In early stages of development -- do not use yet!**

This package implements the claims history simulation algorithm detailed in [*An Individual Claims History Simulation Machine*](https://www.mdpi.com/2227-9091/6/2/29) by Andrea Gabrielli and Mario V. Wüthrich. The goal is to provide an easy-to-use interface for generating claims data that can be used for loss reserving research.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kasaai/conjuror")
devtools::install_github("kasaai/simulationmachine")
```
## Example

First, we can specify the parameters of a simulation using `simulation_machine()`:

```{r}
library(simulationmachine)

incantation <- simulation_machine(
  num_records = 50000, 
  lob_distribution = c(0.25, 0.25, 0.25, 0.25), 
  inflation = c(0.01, 0.01, 0.01, 0.01), 
  sd_claim = 0.85, 
  sd_recovery = 0.85
)

incantation
```

Once we have the incantation object, we can use `conjure()` to perform the simulation.

```{r}
records <- conjure(incantation, seed = 100)
dplyr::glimpse(records)
```
